---
title: "Percent_recruitment"
author: "Joy Buongiorno"
description: "Svalbard MAGs, percent recruitment plot using percent recruitment for bins provided by anvi'o v 7.1 For GitHub Repo (curated from several other exploratory R scripts not publicly available)." 
date: '2022-07-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(dplyr)
library(ggplot2)
library(gplots)
library(reshape)
```

```{r recruitment, bins percentage by phylum}
GTDB_tax<-read.csv("MAG_GTDBtax.csv")
per_recruit<-read.csv("bins_percent_recruitment.csv")
per_recruit_long<-melt(per_recruit)
names(per_recruit_long)[names(per_recruit_long) == "value"] <- "percent_recruitment"
names(per_recruit_long)[names(per_recruit_long) == "variable"] <- "NCBI_name"
per_recruit_long_tax<-left_join(per_recruit_long, GTDB_tax, by = "NCBI_name")
loc<-read.csv("sample_location.csv")
per_recruit_long_tax_loc<-left_join(per_recruit_long_tax,loc, by="samples")

boxplotPal<-c("Proteobacteria"= "#0A4D7C",
              "Desulfobacterota" = "#D6E354",
              "Planctomycetota" = "#F82F06",
              "Bacteroidota" = "#11A896",
              "Actinobacteriota" ="#FF5733",
              "Verrucomicrobiota"="#3386FF", 
              "Chloroflexota" = "#74ff33ff",
              "Myxococcota" = "#F1FE6F",
              "Nitrospinota" = "#6FFEED",
              "BMS3Abin14" = "#808080",
              "Thermoproteota" = "#FFCCCC",
              "Krumholzibacteriota" = "#BB172B",
              "Acidobacteriota" = "#E4A55E",
              "Nitrospirota" = "#205A50",
              "Gemmatimonadota" = "#B9A0CA")
          
  


ggplot(per_recruit_long_tax_loc) +
  geom_bar(aes(x = samples, y = percent_recruitment, fill = Phylum), stat = 'identity', width = 0.5) +
   scale_fill_manual(values=boxplotPal) +
  labs(x = "Sample",
       y = "Percent Recruitment of Transcripts") +
  guides(fill=guide_legend(title="Phylum")) +
  theme_bw() +
  theme(panel.grid.major = element_line(size = 0),
        panel.grid.minor = element_line(size = 0),
        axis.text = element_text(size=15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        strip.text = element_text(size = 20),
        legend.title = element_text(size=15),
        legend.text = element_text(size = 15),
        axis.title = element_text(size=15)) +
  facet_grid(cols=vars(Fjord), scales = "free")
```

ggplot(per_recruit_long_tax_loc) +
  geom_bar(aes(x = samples, y = percent_recruitment, fill = Phylum), stat = 'identity', width = 0.5) +
   scale_fill_manual(values=boxplotPal) +
  labs(x = "Sample",
       y = "Percent Recruitment of Transcripts") +
  guides(fill=guide_legend(title="Phylum")) +
  theme_bw() +
  theme(panel.grid.major = element_line(size = 0),
        panel.grid.minor = element_line(size = 0),
        axis.text = element_text(size=15),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        strip.text = element_text(size = 20),
        legend.title = element_text(size=15),
        legend.text = element_text(size = 15),
        axis.title = element_text(size=15)) +
  facet_grid(cols=vars(Fjord), scales = "free")
```{r summarize, phylum recruitment}
sum_recruit <- per_recruit_long_tax_loc %>%
  group_by(Phylum, Fjord) %>%
  summarize(average = mean(percent_recruitment), max = max(percent_recruitment), min = min(percent_recruitment), sum = sum(percent_recruitment)) 
#write.csv(sum_recruit, "sum_recruit.csv")
```

```{r stats for Bacteriodota}
depth<-read.csv("sample_depth.csv") 
per_recruit_long_tax_loc_depth<-left_join(per_recruit_long_tax_loc, depth, by = "samples")

model<-lm(percent_recruitment ~ Depth, data = per_recruit_long_tax_loc_depth, subset=Phylum == "Bacteroidota")
modsum<-summary(model)
r2 = modsum$adj.r.squared
my.p<-modsum$coefficients[2,4]
plot(subset(per_recruit_long_tax_loc_depth, Phylum == "Bacteroidota", select = c(Depth, percent_recruitment))) + abline(model, col = "red")

rp = vector('expression',2)
rp[1] = substitute(expression(italic(R)^2 == MYVALUE), 
		list(MYVALUE = format(r2,dig=3)))[2]
rp[2] = substitute(expression(italic(p) == MYOTHERVALUE), 
		list(MYOTHERVALUE = format(my.p, digits = 2)))[2]
legend('topright', legend = rp, bty = 'n')

```

```{r stats for Thermoproteota}
model<-lm(percent_recruitment ~ Depth, data = per_recruit_long_tax_loc_depth, subset=Phylum == "Thermoproteota")
modsum<-summary(model)
r2 = modsum$adj.r.squared
my.p<-modsum$coefficients[2,4]
plot(subset(per_recruit_long_tax_loc_depth, Phylum == "Thermoproteota", select = c(Depth, percent_recruitment))) + abline(model, col = "red")

rp = vector('expression',2)
rp[1] = substitute(expression(italic(R)^2 == MYVALUE), 
		list(MYVALUE = format(r2,dig=3)))[2]
rp[2] = substitute(expression(italic(p) == MYOTHERVALUE), 
		list(MYOTHERVALUE = format(my.p, digits = 2)))[2]
legend('topright', legend = rp, bty = 'n')


```

```{r stats for Desulfobacterota, KF }
model<-lm(percent_recruitment ~ Depth, data = per_recruit_long_tax_loc_depth, subset=Phylum == "Desulfobacterota" & Fjord == "Kongsfjorden")
modsum<-summary(model)
r2 = modsum$adj.r.squared
my.p<-modsum$coefficients[2,4]
plot(subset(per_recruit_long_tax_loc_depth, Phylum == "Desulfobacterota" & Fjord == "Kongsfjorden", select = c(Depth, percent_recruitment))) + abline(model, col = "red")

rp = vector('expression',2)
rp[1] = substitute(expression(italic(R)^2 == MYVALUE), 
		list(MYVALUE = format(r2,dig=3)))[2]
rp[2] = substitute(expression(italic(p) == MYOTHERVALUE), 
		list(MYOTHERVALUE = format(my.p, digits = 2)))[2]
legend('topright', legend = rp, bty = 'n')


```

```{r stats for Desulfobacterota, VK }
model<-lm(percent_recruitment ~ Depth, data = per_recruit_long_tax_loc_depth, subset=Phylum == "Desulfobacterota" & Fjord == "Van Keulenfjorden")
modsum<-summary(model)
r2 = modsum$adj.r.squared
my.p<-modsum$coefficients[2,4]
plot(subset(per_recruit_long_tax_loc_depth, Phylum == "Desulfobacterota" & Fjord == "Van Keulenfjorden", select = c(Depth, percent_recruitment))) + abline(model, col = "red")

rp = vector('expression',2)
rp[1] = substitute(expression(italic(R)^2 == MYVALUE), 
		list(MYVALUE = format(r2,dig=3)))[2]
rp[2] = substitute(expression(italic(p) == MYOTHERVALUE), 
		list(MYOTHERVALUE = format(my.p, digits = 2)))[2]
legend('topright', legend = rp, bty = 'n')


```
